Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/intro.tex
Fei's latest comments
Dan's statistics, Vidya's interactivity, column balancing

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as Polaris~\cite{Stolte:2008} and Spotfire~\cite{Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have both the domain knowledge and the ability to process data in parallel by using their visual systems \cite{Cleveland.McGill1984,Mackinlay:1986}. Humans also provide the definition of what is valuable in an analysis. Algorithms that rely on \emph{both} the processing capability of computer systems and human feedback, are more effective in extracting useful knowledge from the large amounts of data being generated.
\vidya{still struggling to understand how interactivity is relevant to what we're doing here...}

@@

One of the most common data preparation tasks we see users performing is the parsing of date strings into scalar date representations, and streamlining this process is the focus of this paper \vidya{do we have any data to backup this?}\richard{Yes, I think Dan has some}. We now provide some background on the use of dates in data analytics to provide context for the problem.

@@

And this is but a single date format. Our studies of online data collections suggest that there are hundreds of distinct temporal date formats in user data sets. Some are common, but others can be quite idiosyncratic. Table 1 shows a selection of unusual date formats found in our corpus (the meanings of the ICU formatting codes can be found in Table 2). The first example shows a time zone in the middle of the date and a year after the time; the second shows a leading unmatched bracket and a colon between the date and time components; the third shows confusion between the seconds' decimal point and the time part delimiter; the fourth shows a two digit year apostrophe on a four digit year and the fifth shows a dash separating the date and time components.

>>>>

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as Polaris~\cite{Stolte:2008} and Spotfire~\cite{Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have both the domain knowledge and the ability to process data in parallel by using their visual systems \cite{Cleveland.McGill1984,Mackinlay:1986}. Humans also provide the definition of what is valuable in an analysis. Systems that rely on \emph{both} the processing capability of computer systems and human feedback, are more effective in extracting useful knowledge from the large amounts of data being generated than either by itself.

@@

One of the most common data preparation tasks we see users performing is the parsing of date strings into scalar date representations, 
and streamlining this process is the focus of this paper. An examination of the author calculations in an online repository of our
visualization system shows that there are about as many workbooks containing date parsing calculations ($3.3\%$) as there are
 integer type conversions of any kind ($3.4\%$).
We now provide some background on the use of dates in data analytics to provide context for the problem.

@@

And this is but a single date format. Our studies of online data collections suggest that there are hundreds of distinct temporal date formats in user data sets. Some are common, but others can be quite idiosyncratic. Table 1 shows a selection of unusual date formats found in our corpus (the meanings of the ICU formatting codes can be found in Table 2). The first example shows a time zone in the middle of the date and a year after the time; the second shows a leading unmatched bracket and a colon between the date and time components; the third shows confusion between the seconds' decimal point and the time part delimiter; the fourth shows a two digit year apostrophe on a four digit year and the fifth shows a dash separating the date and time components. 
As can be seen in Figure \ref{fig:M2}, the long tail of formats means that these idiosyncrasies are the rule, not the exception, 
so a static enumeration of a small set of formats will not produce high reliability.
